```{r}
library(pacman)
#p_load(data.table, dplyr, ggplot2, rtracklayer, RColorBrewer, scales, foreach, GenomicRanges, clusterProfiler, doParallel, 
#viridis, annotatr, stringr, GGally, EnrichedHeatmap, circlize, corrplot, patchwork, org.Mm.eg.db, ggvenn)

p_load(data.table, dplyr, ggplot2, RColorBrewer, patchwork, scales, svglite, org.Mm.eg.db, GenomicRanges, foreach, clusterProfiler, ggthemes, rtracklayer, stringr)

options(scipen=999)
knitr::opts_chunk$set(fig.width=9, fig.height=7)
dir.create(outdatadir, recursive=TRUE)
source("./code/common.R")
#registerDoParallel(6)
```

# STUFF {.tabset}  

BlackListed regions are present/counted.  

```{r}
tmp <- readRDS(paste0("output/code/PrepAllData//WGBS_vs_RRBS_data.RDS"))
met_gr <- tmp[["methylation_gr_th"]]
met_gr <- met_gr[seqnames(met_gr) %in% paste0("chr", c(1:19, "X", "Y"))]

th <- 0.75

th_WGBS_KO_met <- quantile(mcols(met_gr)$WGBS_KO_met, th, na.rm=TRUE)
th_WGBS_homo_met <- quantile(mcols(met_gr)$WGBS_homo_met, th, na.rm=TRUE)
th_WGBS_hetero_met <- quantile(mcols(met_gr)$WGBS_hetero_met, th, na.rm=TRUE)
th_WGBS_WT_met <- quantile(mcols(met_gr)$WGBS_WT_met, th, na.rm=TRUE)

met_gr_mod <- copy(met_gr)
mcols(met_gr_mod)$WGBS_homo_met[mcols(met_gr_mod)$WGBS_homo_met < th_WGBS_homo_met] <- 0
mcols(met_gr_mod)$WGBS_hetero_met[mcols(met_gr_mod)$WGBS_hetero_met < th_WGBS_hetero_met] <- 0
mcols(met_gr_mod)$WGBS_WT_met[mcols(met_gr_mod)$WGBS_WT_met < th_WGBS_WT_met] <- 0
mcols(met_gr_mod)$WGBS_KO_met[mcols(met_gr_mod)$WGBS_KO_met < th_WGBS_KO_met] <- 0

tmp <- readRDS(paste0("output/code/PrepAllData//dAnnotations.RDS"))
repeatai <- tmp[["repeatai"]]
mcols(repeatai)$type <- paste0(mcols(repeatai)$Name, "_", mcols(repeatai)$Class, "_", mcols(repeatai)$Familly)
annotations <- tmp[["anotacijos"]]
annotations <- annotations[seqnames(annotations) %in% paste0("chr", c(1:19, "X", "Y"))]
anotacijos <- c(annotations, repeatai)

rm(tmp)
gc()
samples2do_BS <- c("WGBS_KO_met", "WGBS_hetero_met", "WGBS_homo_met", "WGBS_WT_met")
```


## CG level TOP25

CG that were not 0 in WT are not used here (calculated as 0). 
Mean per replicate plotted.

```{r, fig.height=7}
coverages2 <- copy(met_gr_mod)

gff <- import("/mnt/store/annotations/MusMusculus_mm10_Ensembl/ENCODE/gencode.vM23.annotation.gtf")

# darom nauja anotacija 

tmp <- annotations[mcols(annotations)$type == "mm10_genes_3UTRs"]
mcols(tmp)$type <- "3UTRs"
tmp_annotations <- copy(tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_genes_5UTRs"]
mcols(tmp)$type <- "5UTRs"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_lncrna_gencode"]
mcols(tmp)$type <- "lncRNA_gencode"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_genes_exons"]
mcols(tmp)$type <- "exons"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_genes_introns"]
mcols(tmp)$type <- "introns"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_EPDpromoters"]
mcols(tmp)$type <- "promoterEPD"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_EPDpromotersNC"]
mcols(tmp)$type <- "promoter_NC_EPD"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_transcriptsCoding"]
mcols(tmp)$type <- "codingTranscripts"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"][countOverlaps(annotations[mcols(annotations)$type == "mm10_cpg_islands"], annotations[mcols(annotations)$type == "mm10_EPDpromoters"]) > 0]
mcols(tmp)$type <- "CGI promoter"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"][countOverlaps(annotations[mcols(annotations)$type == "mm10_cpg_islands"], annotations[mcols(annotations)$type == "mm10_genes_intergenic"]) > 0]
mcols(tmp)$type <- "CGI intergenic"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"][countOverlaps(annotations[mcols(annotations)$type == "mm10_cpg_islands"], annotations[mcols(annotations)$type == "mm10_transcriptsCoding"]) > 0]
mcols(tmp)$type <- "CGI intragenic"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_shelves"]
mcols(tmp)$type <- "CGI shelves"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_shores"]
mcols(tmp)$type <- "CGI shores"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"]
mcols(tmp)$type <- "CGI all"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- gff[mcols(gff)$gene_type == "miRNA"] 
mcols(tmp) <- NULL 
mcols(tmp)$type <- "miRNA"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- gff[mcols(gff)$gene_type == "snoRNA"]
mcols(tmp) <- NULL 
mcols(tmp)$type <- "snoRNA"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- gff[mcols(gff)$gene_type == "snRNA"]
mcols(tmp) <- NULL 
mcols(tmp)$type <- "snRNA"
tmp_annotations <- c(tmp_annotations, tmp)

elements2do <- c("3UTRs", "5UTRs", "lncRNA_gencode", "exons", "introns", "promoterEPD", "promoter_NC_EPD", "codingTranscripts", "CGI promoter", "CGI intergenic", "CGI intragenic", "CGI shelves", "CGI shores", "CGI all", "miRNA", "snoRNA", "snRNA")


do_enrichment <- function(featuras, samplas, annotation=annotations, covai=coverages)  {
#  featuras <- "mm10_cpg_islands"
#  samplas <- "Hom_R1"
  
  if(!(file.exists(paste0(outdatadir, "Enri_", featuras, "_", samplas, "_25.RDS")))) {
    anno <- annotation[annotation$type == featuras]
    covai <-  covai[!is.na(elementMetadata(covai)[, samplas]), ]
    meginys_pos <- covai[elementMetadata(covai)[, samplas]>0]
    meginys_neg <- covai[elementMetadata(covai)[, samplas]==0]
    in_cat_pos <- sum(countOverlaps(meginys_pos, anno)>0)
    in_cat_neg <- sum(countOverlaps(meginys_neg, anno)>0)
    not_cat_pos <- sum(countOverlaps(meginys_pos, anno)==0)
    not_cat_neg <- sum(countOverlaps(meginys_neg, anno)==0)
    d <- data.frame(CG_interest=c(in_cat_pos, not_cat_pos), CG_not_interest=c(in_cat_neg, not_cat_neg))  
    fi <- fisher.test(d)
    rezu <- data.table(Pval=fi$p.value, Enri=fi$estimate, Elem=featuras, Sample=samplas, Ntarget=length(meginys_pos))
    saveRDS(rezu, paste0(outdatadir, "Enri_", featuras, "_", samplas, "_25.RDS"))
    return(rezu)
  } else {tmp <- readRDS(paste0(outdatadir, "Enri_", featuras, "_", samplas, "_25.RDS")); return(tmp)}
} 


enri <- foreach(i=samples2do_BS, .combine="rbind") %dopar% {
  ret <- foreach(j=elements2do, .combine="rbind") %do% {
    ret <- do_enrichment(j, i, annotation=tmp_annotations, covai=coverages2)
    return(ret) }
  return(ret)  
} %>% 
  .[Pval <= 0.05, ] %>% 
  .[, replicate := str_extract( Sample, "R[0-9]")]  %>% 
  .[, type := strsplit(Sample, "_") %>% sapply(., `[`, 1)]  %>% 
  .[, Enri := Enri] 



enri %>% 
#  .[, Elem := factor(Elem, levels=tvarka)] %>%
  ggplot(aes(Elem, Enri, fill=type)) +
    geom_point(shape=21, size=2) +
    coord_flip() +
    theme_Publication() +
    scale_fill_manual(values=cols_samples) 

enri_genomic <- copy(enri)    
```

```{r, fig.height=4}
tmp <- repeatai[mcols(repeatai)$Class == "DNA"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "DNA"
tmp_annotations <- copy(tmp)

tmp <- repeatai[mcols(repeatai)$Class == "SINE"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "SINE"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "LINE"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "LINE"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "LTR"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "LTR"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "Simple_repeat"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "Simples"
tmp_annotations <- c(tmp_annotations, tmp)


tmp <- repeatai[mcols(repeatai)$Class == "Satellite"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "Satellite"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "Low_complexity"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "Low_complexity"
tmp_annotations <- c(tmp_annotations, tmp)

reps2do <- c("DNA", "SINE", "LINE", "LTR", "Simples", "Satellite", "Low_complexity")

enri <- foreach(i=samples2do_BS, .combine="rbind") %dopar% {
  ret <- foreach(j=reps2do, .combine="rbind") %do% {
    ret <- do_enrichment(j, i, tmp_annotations, covai=coverages2)
    return(ret) }
  return(ret)  
} %>% 
  .[Pval <= 0.05, ] %>% 
  .[, replicate := str_extract( Sample, "R[0-9]")]  %>% 
  .[, type := strsplit(Sample, "_") %>% sapply(., `[`, 1)]  %>% 
  .[, Enri := Enri] 



enri %>% 
  #.[, Elem := factor(Elem, levels=tvarka)] %>%
  ggplot(aes(Elem, Enri, fill=type)) +
    geom_point(shape=21, size=2) +
    coord_flip() +
    theme_Publication() +
    scale_fill_manual(values=cols_samples) 

```

Tas pats, kas viršuje, bet sudėta kartu

```{r}
d <- rbind(enri, enri_genomic)

#tvarka <- d %>% .[type == "Hom", ] %>% setorder(., Enri) %>% .[, Elem]

#temp <- d %>% 
#  .[, Elem := factor(Elem, levels=tvarka)] 

saveRDS(d, paste0(outdatadir, "Enrichment_CG_025.RDS"))

ggplot(d, aes(Elem, Enri, fill=type)) +
  geom_point(shape=21, size=2) +
  coord_flip() +
  theme_Publication() +
  scale_fill_manual(values=cols_samples) 
```

## Enrichment Promoters TOP25

Enrichment (GO BP). There were no results with WT. 
0.001 threshold was applied. 

```{r,  fig.width=9, fig.height=15}
coverages <- copy(met_gr_mod) 
cov_CGI <- coverages[countOverlaps(coverages, annotations[annotations$type == "mm10_cpg_islands"]) > 0, ]
promotoriai <- annotations[annotations$type == "mm10_EPDpromoters"]

tmp <- foreach(i=samples2do_BS) %do% {
  cov_CGI2 <- cov_CGI[!is.na(elementMetadata(cov_CGI)[, i]), ]
  sam2do <- cov_CGI2[elementMetadata(cov_CGI2)[, i] > 0]
  fo <- findOverlaps(promotoriai, sam2do)
  return(promotoriai[queryHits(fo)]$gene_id %>% unique) 
}
names(tmp) <- samples2do_BS
WT_genes <- tmp$WGBS_WT_met
Het_genes <- tmp$WGBS_hetero_met 
Hom_genes <- tmp$WGBS_homo_met
KO_genes <- tmp$WGBS_KO_met

listas <- list(Hetero=Het_genes, Homo=Hom_genes, WT=WT_genes, KO=KO_genes)

if(!file.exists(paste0(outdatadir, "promoterEnri_25.RDS"))) {
ck <- compareCluster(geneCluster = listas, 
                     fun = enrichGO, universe = promotoriai$gene_id, 
                     OrgDb = org.Mm.eg.db, readable = TRUE, 
                     pvalueCutoff  = 0.001,
                     qvalueCutoff  = 0.001,
                     pAdjustMethod = "BH",
                     keyType = "ENSEMBL", ont = "BP")
saveRDS(ck, paste0(outdatadir, "promoterEnri_25.RDS")) } else {ck <- readRDS(paste0(outdatadir, "promoterEnri_25.RDS"))}
dotplot(ck, show=50)
```


## CG level TOP 10


```{r}
tmp <- readRDS(paste0("output/code/PrepAllData//WGBS_vs_RRBS_data.RDS"))
met_gr <- tmp[["methylation_gr_th"]]
met_gr <- met_gr[seqnames(met_gr) %in% paste0("chr", c(1:19, "X", "Y"))]

th <- 0.9

th_WGBS_KO_met <- quantile(mcols(met_gr)$WGBS_KO_met, th, na.rm=TRUE)
th_WGBS_homo_met <- quantile(mcols(met_gr)$WGBS_homo_met, th, na.rm=TRUE)
th_WGBS_hetero_met <- quantile(mcols(met_gr)$WGBS_hetero_met, th, na.rm=TRUE)
th_WGBS_WT_met <- quantile(mcols(met_gr)$WGBS_WT_met, th, na.rm=TRUE)

met_gr_mod <- copy(met_gr)
mcols(met_gr_mod)$WGBS_homo_met[mcols(met_gr_mod)$WGBS_homo_met < th_WGBS_homo_met] <- 0
mcols(met_gr_mod)$WGBS_hetero_met[mcols(met_gr_mod)$WGBS_hetero_met < th_WGBS_hetero_met] <- 0
mcols(met_gr_mod)$WGBS_WT_met[mcols(met_gr_mod)$WGBS_WT_met < th_WGBS_WT_met] <- 0
mcols(met_gr_mod)$WGBS_KO_met[mcols(met_gr_mod)$WGBS_KO_met < th_WGBS_KO_met] <- 0

tmp <- readRDS(paste0("output/code/PrepAllData//dAnnotations.RDS"))
repeatai <- tmp[["repeatai"]]
mcols(repeatai)$type <- paste0(mcols(repeatai)$Name, "_", mcols(repeatai)$Class, "_", mcols(repeatai)$Familly)
annotations <- tmp[["anotacijos"]]
annotations <- annotations[seqnames(annotations) %in% paste0("chr", c(1:19, "X", "Y"))]
anotacijos <- c(annotations, repeatai)

rm(tmp)
gc()
samples2do_BS <- c("WGBS_KO_met", "WGBS_hetero_met", "WGBS_homo_met", "WGBS_WT_met")
```


## CG level TOP25

CG that were not 0 in WT are not used here (calculated as 0). 
Mean per replicate plotted.

```{r, fig.height=7}
coverages2 <- copy(met_gr_mod)

gff <- import("/mnt/store/annotations/MusMusculus_mm10_Ensembl/ENCODE/gencode.vM23.annotation.gtf")

# darom nauja anotacija 

tmp <- annotations[mcols(annotations)$type == "mm10_genes_3UTRs"]
mcols(tmp)$type <- "3UTRs"
tmp_annotations <- copy(tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_genes_5UTRs"]
mcols(tmp)$type <- "5UTRs"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_lncrna_gencode"]
mcols(tmp)$type <- "lncRNA_gencode"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_genes_exons"]
mcols(tmp)$type <- "exons"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_genes_introns"]
mcols(tmp)$type <- "introns"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_EPDpromoters"]
mcols(tmp)$type <- "promoterEPD"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_EPDpromotersNC"]
mcols(tmp)$type <- "promoter_NC_EPD"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_transcriptsCoding"]
mcols(tmp)$type <- "codingTranscripts"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"][countOverlaps(annotations[mcols(annotations)$type == "mm10_cpg_islands"], annotations[mcols(annotations)$type == "mm10_EPDpromoters"]) > 0]
mcols(tmp)$type <- "CGI promoter"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"][countOverlaps(annotations[mcols(annotations)$type == "mm10_cpg_islands"], annotations[mcols(annotations)$type == "mm10_genes_intergenic"]) > 0]
mcols(tmp)$type <- "CGI intergenic"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"][countOverlaps(annotations[mcols(annotations)$type == "mm10_cpg_islands"], annotations[mcols(annotations)$type == "mm10_transcriptsCoding"]) > 0]
mcols(tmp)$type <- "CGI intragenic"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_shelves"]
mcols(tmp)$type <- "CGI shelves"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_shores"]
mcols(tmp)$type <- "CGI shores"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"]
mcols(tmp)$type <- "CGI all"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- gff[mcols(gff)$gene_type == "miRNA"] 
mcols(tmp) <- NULL 
mcols(tmp)$type <- "miRNA"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- gff[mcols(gff)$gene_type == "snoRNA"]
mcols(tmp) <- NULL 
mcols(tmp)$type <- "snoRNA"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- gff[mcols(gff)$gene_type == "snRNA"]
mcols(tmp) <- NULL 
mcols(tmp)$type <- "snRNA"
tmp_annotations <- c(tmp_annotations, tmp)

elements2do <- c("3UTRs", "5UTRs", "lncRNA_gencode", "exons", "introns", "promoterEPD", "promoter_NC_EPD", "codingTranscripts", "CGI promoter", "CGI intergenic", "CGI intragenic", "CGI shelves", "CGI shores", "CGI all", "miRNA", "snoRNA", "snRNA")


do_enrichment <- function(featuras, samplas, annotation=annotations, covai=coverages)  {
#  featuras <- "mm10_cpg_islands"
#  samplas <- "Hom_R1"
  
  if(!(file.exists(paste0(outdatadir, "Enri_", featuras, "_", samplas, "_10.RDS")))) {
    anno <- annotation[annotation$type == featuras]
    covai <-  covai[!is.na(elementMetadata(covai)[, samplas]), ]
    meginys_pos <- covai[elementMetadata(covai)[, samplas]>0]
    meginys_neg <- covai[elementMetadata(covai)[, samplas]==0]
    in_cat_pos <- sum(countOverlaps(meginys_pos, anno)>0)
    in_cat_neg <- sum(countOverlaps(meginys_neg, anno)>0)
    not_cat_pos <- sum(countOverlaps(meginys_pos, anno)==0)
    not_cat_neg <- sum(countOverlaps(meginys_neg, anno)==0)
    d <- data.frame(CG_interest=c(in_cat_pos, not_cat_pos), CG_not_interest=c(in_cat_neg, not_cat_neg))  
    fi <- fisher.test(d)
    rezu <- data.table(Pval=fi$p.value, Enri=fi$estimate, Elem=featuras, Sample=samplas, Ntarget=length(meginys_pos))
    saveRDS(rezu, paste0(outdatadir, "Enri_", featuras, "_", samplas, "_10.RDS"))
    return(rezu)
  } else {tmp <- readRDS(paste0(outdatadir, "Enri_", featuras, "_", samplas, "_10.RDS")); return(tmp)}
} 


enri <- foreach(i=samples2do_BS, .combine="rbind") %dopar% {
  ret <- foreach(j=elements2do, .combine="rbind") %do% {
    ret <- do_enrichment(j, i, annotation=tmp_annotations, covai=coverages2)
    return(ret) }
  return(ret)  
} %>% 
  .[Pval <= 0.05, ] %>% 
  .[, replicate := str_extract( Sample, "R[0-9]")]  %>% 
  .[, type := strsplit(Sample, "_") %>% sapply(., `[`, 1)]  %>% 
  .[, Enri := Enri] 



enri %>% 
#  .[, Elem := factor(Elem, levels=tvarka)] %>%
  ggplot(aes(Elem, Enri, fill=type)) +
    geom_point(shape=21, size=2) +
    coord_flip() +
    theme_Publication() +
    scale_fill_manual(values=cols_samples) 

enri_genomic <- copy(enri)    
```

```{r, fig.height=4}
tmp <- repeatai[mcols(repeatai)$Class == "DNA"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "DNA"
tmp_annotations <- copy(tmp)

tmp <- repeatai[mcols(repeatai)$Class == "SINE"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "SINE"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "LINE"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "LINE"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "LTR"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "LTR"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "Simple_repeat"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "Simples"
tmp_annotations <- c(tmp_annotations, tmp)


tmp <- repeatai[mcols(repeatai)$Class == "Satellite"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "Satellite"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "Low_complexity"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "Low_complexity"
tmp_annotations <- c(tmp_annotations, tmp)

reps2do <- c("DNA", "SINE", "LINE", "LTR", "Simples", "Satellite", "Low_complexity")

enri <- foreach(i=samples2do_BS, .combine="rbind") %dopar% {
  ret <- foreach(j=reps2do, .combine="rbind") %do% {
    ret <- do_enrichment(j, i, tmp_annotations, covai=coverages2)
    return(ret) }
  return(ret)  
} %>% 
  .[Pval <= 0.05, ] %>% 
  .[, replicate := str_extract( Sample, "R[0-9]")]  %>% 
  .[, type := strsplit(Sample, "_") %>% sapply(., `[`, 1)]  %>% 
  .[, Enri := Enri] 



enri %>% 
  #.[, Elem := factor(Elem, levels=tvarka)] %>%
  ggplot(aes(Elem, Enri, fill=type)) +
    geom_point(shape=21, size=2) +
    coord_flip() +
    theme_Publication() +
    scale_fill_manual(values=cols_samples) 

```

Tas pats, kas viršuje, bet sudėta kartu

```{r}
d <- rbind(enri, enri_genomic)

saveRDS(d, paste0(outdatadir, "Enrichment_CG_10.RDS"))

ggplot(d, aes(Elem, Enri, fill=type)) +
  geom_point(shape=21, size=2) +
  coord_flip() +
  theme_Publication() +
  scale_fill_manual(values=cols_samples) 
```

## Enrichment Promoters TOP10

Enrichment (GO BP). There were no results with WT. 
0.001 threshold was applied. 

```{r,  fig.width=9, fig.height=15}
coverages <- copy(met_gr_mod) 
cov_CGI <- coverages[countOverlaps(coverages, annotations[annotations$type == "mm10_cpg_islands"]) > 0, ]
promotoriai <- annotations[annotations$type == "mm10_EPDpromoters"]

tmp <- foreach(i=samples2do_BS) %do% {
  cov_CGI2 <- cov_CGI[!is.na(elementMetadata(cov_CGI)[, i]), ]
  sam2do <- cov_CGI2[elementMetadata(cov_CGI2)[, i] > 0]
  fo <- findOverlaps(promotoriai, sam2do)
  return(promotoriai[queryHits(fo)]$gene_id %>% unique) 
}
names(tmp) <- samples2do_BS
WT_genes <- tmp$WGBS_WT_met
Het_genes <- tmp$WGBS_hetero_met 
Hom_genes <- tmp$WGBS_homo_met
KO_genes <- tmp$WGBS_KO_met

listas <- list(Hetero=Het_genes, Homo=Hom_genes, WT=WT_genes, KO=KO_genes)

if(!file.exists(paste0(outdatadir, "promoterEnri_10.RDS"))) {
ck <- compareCluster(geneCluster = listas, 
                     fun = enrichGO, universe = promotoriai$gene_id, 
                     OrgDb = org.Mm.eg.db, readable = TRUE, 
                     pvalueCutoff  = 0.001,
                     qvalueCutoff  = 0.001,
                     pAdjustMethod = "BH",
                     keyType = "ENSEMBL", ont = "BP")
saveRDS(ck, paste0(outdatadir, "promoterEnri_10.RDS")) } else {ck <- readRDS(paste0(outdatadir, "promoterEnri_10.RDS"))}
dotplot(ck, show=50)
```
