```{r}
library(pacman)
p_load(data.table, dplyr, ggplot2, rtracklayer, RColorBrewer, scales, foreach, doParallel, org.Mm.eg.db,
viridis, annotatr, stringr, patchwork, GGally, EnrichedHeatmap, circlize, clusterProfiler)
options(scipen=999)
dir.create(outdatadir, recursive=TRUE)
registerDoParallel(20)
source("./code/common.R")
knitr::opts_chunk$set(fig.width=9, fig.height=5)
```

# TopSeq {.tabset}

Basic statistics. 

```{r}
configs <- fread("data_prep/config_torrent.yaml", header=FALSE) 
wdir <- configs[V1 == "workdir:", V2]

samplesInfo <- fread("input/samples_info.txt") %>% 
  .[USE == "E2", ] %>% 
  .[, replicate := str_extract(ID, "R.$")] %>% 
  .[, condition := gsub("_R[0-9]", "", ID)] %>% 
  .[ID != "Het_R1", ]
samples2do <- samplesInfo$ID
samples2do_m <- c("WT", "Het", "Hom")
```
 
```{r}
coverages <- readRDS("./output/code/PrepAllData/mutantai_coverages2useTopData.RDS")
```

## Simple stats 

Usefull reads number, number of targets, mean/median coverage, distance to targets. 

Number of reads (only reads that were assigned to targets counted).
```{r}
coverages[, samples2do, with=FALSE] %>% 
  colSums() %>% 
  as.data.frame() %>% 
  as.data.table(., keep.rownames=TRUE) %>% 
  melt() %>% 
  as.data.table() %>% 
  .[, variable := NULL] %>% 
  ggplot(aes(rn, value, label=paste0(round(value/1000000, 2), "M"))) +  
    geom_col(position="dodge") +
    geom_text(aes(angle=90)) +
    theme_bw() +
    ggtitle("Read count") +
    ylab("Reads") + 
    scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) +
    theme(axis.title.x = element_blank())
```

Number of targets (coverage at least 1)

```{r}
get_targets <- function(x, th=0) {sum(x>th)}
coverages[, samples2do, with=FALSE] %>% 
  apply(., 2, get_targets) %>% 
  as.data.frame() %>% 
  as.data.table(., keep.rownames=TRUE) %>% 
  melt() %>% 
  as.data.table() %>% 
  .[, variable := NULL] %>% 
  ggplot(aes(rn, value, label=paste0(round(value/1000000, 2), "M"))) +  
    geom_col(position="dodge") +
    geom_text(aes(angle=90)) +
    theme_bw() +
    ggtitle("Target count") +
    ylab("Targets") + 
    scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) +
    theme(axis.title.x = element_blank())

temp <- coverages[, c(samples2do_m, samples2do), with=FALSE] %>% 
  apply(., 2, get_targets) %>% 
  as.data.frame() %>% 
  as.data.table(., keep.rownames=TRUE) %>% 
  melt() %>% 
  as.data.table() %>% 
  .[, variable := NULL]

saveRDS(temp, paste0(outdatadir, "data_TargetNo.RDS"))
```

Average and median coverage of all targets that were covered with at least on read. 

```{r}
covas <- function(x) {mean(x[x>0])}
coverages[, samples2do, with=FALSE] %>% 
  apply(., 2, covas) %>% 
  as.data.table(., keep.rownames=TRUE) %>% 
  melt() %>% 
  ggplot(aes(rn, value))+
    geom_col() +
    theme_bw() +
    ggtitle("Average coverage") +
    xlab("sample") +
    ylab("coverage")

temp <- coverages[, c(samples2do_m, samples2do), with=FALSE] %>% 
  apply(., 2, covas) %>% 
  as.data.table(., keep.rownames=TRUE) %>% 
  melt()

saveRDS(temp, paste0(outdatadir, "data_TargetCov.RDS"))

medianas <- function(x) {median(x[x>0])}
coverages[, samples2do, with=FALSE] %>% 
  apply(., 2, medianas) %>% 
  as.data.table(., keep.rownames=TRUE) %>% 
  melt() %>% 
  ggplot(aes(rn, value))+
    geom_col() +
    theme_bw() +
    ggtitle("Median coverage") +
    xlab("sample") +
    ylab("coverage")
```

Number of targets with specific coverage. 

```{r}
cum_cov <- function(x) {
  rez <- foreach(i=1:10, .combine="rbind") %do% {
    sum(x==i) 
  }
  rbind(rez, sum(x>10)) 
}
coverages[, samples2do, with=FALSE] %>% 
  apply(., 2, cum_cov) %>% 
  as.data.table(., keep.rownames=TRUE) %>% 
  .[, nr := 1:11] %>% 
  melt(, id.vars="nr") %>% 
  .[, nr := factor(nr, levels=1:11, labels=c(1:10, ">10"))] %>% 
  ggplot(aes(nr, value)) +
    geom_col() +
    theme_bw() +
    ggtitle("Number of targets") +
    xlab("sample") +
    ylab("Coverage == X") +
    scale_y_continuous(labels = label_number(suffix = " K", scale = 1e-3)) +
    facet_wrap(~variable, scales="free")
```

Coverage density. Empty (zero coverage) CGs were removed. Values higher than 50 
were transformed to 50. All values log2 transformed. 

```{r}
coverages[, samples2do, with=FALSE] %>% 
  melt() %>% 
  as.data.table() %>% 
  .[value > 0, ] %>% 
  .[value > 50, value := 50] %>% 
  .[, value := log2(value)] %>% 
  .[, condition :=  strsplit(as.character(variable), "_") %>% sapply(., `[`, 1)] %>% 
  ggplot(aes(x=value, fill=variable, colour=variable)) +
    geom_density(key_glyph = "rect", alpha=0.5) +
    theme_bw() +
    ggtitle("Coverage density") +
    scale_colour_brewer(palette="Paired") +
    scale_fill_brewer(palette="Paired") +
    facet_wrap(~condition) +
    theme(legend.position="bottom") +
    xlab("log2(coverage)")

coverages[, samples2do, with=FALSE] %>% 
  melt() %>% 
  as.data.table() %>% 
  .[value > 0, ] %>% 
  .[value > 50, value := 50] %>% 
  .[, value := log2(value)] %>% 
  ggplot(aes(x=value, fill=variable, colour=variable)) +
    geom_density(key_glyph = "rect", alpha=0.5) +
    theme_bw() +
    ggtitle("Coverage density") +
    scale_colour_brewer(palette="Dark2") +
    scale_fill_brewer(palette="Dark2") +
    theme(legend.position="bottom") +
    xlab("log2(coverage)")    
```

Distance to nearest target. 
```{r}
d <- readRDS(paste0("./output/code/PrepAllData/", "mutantai_TopData.RDS"))
atstumai <- foreach(i=names(d), .combine="rbind") %do% {
  d[[i]][[1]] %>% 
    as.data.table %>% 
    .[, grupe := "KITA"] %>% 
    as.data.table %>% 
    .[, V1 := as.numeric(V1)] %>% 
    .[V1 ==  -1, grupe := "-1"] %>% 
    .[V1 == -2, grupe := "-2"] %>% 
    .[V1 == -3, grupe := "-3"] %>% 
    .[V1 == -4, grupe := "-4"] %>%
    .[V1 == -5, grupe := "-5"] %>% 
    .[V1 == -6, grupe := "-6"] %>% 
    .[V1 == -7, grupe := "-7"] %>% 
    .[V1 < -7, grupe := "<=-8"] %>% 
    .[V1 == 1, grupe := "1"] %>% 
    .[V1 == 2, grupe := "2"] %>% 
    .[V1 == 3, grupe := "3"] %>% 
    .[V1 == 4, grupe := "4"] %>%
    .[V1 == 5, grupe := "5"] %>% 
    .[V1 == 6, grupe := "6"] %>% 
    .[V1 == 7, grupe := "7"] %>% 
    .[V1 > 7, grupe := ">=8"] %>% 
    .[V1 == 0, grupe := 0] %>% 
    .[, lapply(.SD, sum), by="grupe", .SDcols="N"] %>% 
    .[, grupe := factor(grupe, levels=c("<=-8", "-7", "-6", "-5",  "-4", "-3", "-2", "-1", "0", "1", "2", "3", "4", "5", "6", "7", ">=8"))] %>% 
    .[, name := i] %>% 
    .[]
}

atstumai %>% as.data.table() %>% 
  .[, condition := strsplit(name, "_") %>% sapply(., `[`, 1)] %>% 
  ggplot(aes(grupe, N, group=name, color=name)) +
    geom_point() +
    geom_line() +
    theme_bw() +
    facet_wrap(~name, scales="free") +
    ylab("Number of reads") +
    xlab("Distance to CG target") +
    facet_wrap(~condition, scales="free") +
    scale_colour_brewer(palette="Paired") +
    scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) +
    theme(legend.position="bottom") +
    labs(color="Sample")

total <- atstumai %>% 
  as.data.table() %>% 
  .[, condition := strsplit(name, "_") %>% sapply(., `[`, 1)] %>% 
  .[, lapply(.SD, sum), by=c("condition"), .SDcols="N"] %>% setnames(., c("condition", "total"))

atstumai %>%  
  as.data.table() %>% 
  .[, condition := strsplit(name, "_") %>% sapply(., `[`, 1)] %>% 
  .[, lapply(.SD, sum), by=c("condition", "grupe"), .SDcols="N"] %>% 
  merge(., total, by="condition") %>% 
  .[, frac := N/total] %>% 
  ggplot(aes(grupe, frac, colour=condition, group=condition)) +
    geom_point() +
    geom_line() +
    theme_bw() +
    scale_colour_brewer(palette="Dark2") +
    theme(legend.position="bottom") +
    labs(color="Sample") +
    ylab("Fraction of reads, %") +
    scale_y_continuous(labels = scales::percent) +
    xlab("Distance to CpG, bp")
```

## Per chromosome stats 

```{r}
tmp <- foreach(i=samples2do_m, .combine="rbind") %do% {
  coverages[, c("chr", i), with=FALSE] %>% 
    .[get(i) > 0,] %>% 
    setnames(., c("chr", "coverage")) %>% 
    .[, sample := i] %>% 
    .[]    
} %>% 
  as.data.table() %>% 
  .[, chr := factor(chr, levels=paste0("chr", c(1:19, "X", "Y")))] 

ggplot(tmp, aes(chr, coverage, fill=sample)) +
  geom_boxplot(outlier.shape=NA) +
  theme_bw() +
  scale_fill_brewer(palette="Dark2") +
  coord_cartesian(ylim=c(0, 35)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ylab("coverage, fold") +
  ggtitle("Coverage per chromosome")

saveRDS(tmp, paste0(outdatadir, "data_perChromCoverage.RDS"))

tmp <- foreach(i=samples2do_m, .combine="rbind") %do% {
  coverages[, c("chr", i), with=FALSE] %>% 
    .[get(i) > 0, chr] %>% 
    table %>% 
    as.data.table(., keep.rownames=TRUE) %>%
    setnames(., c("chr", "targets")) %>% 
    .[, sample := i] %>% 
    .[]    
} %>% 
  as.data.table() %>% 
  merge(., (table(coverages$chr) %>% as.data.table(., keep.rownames=TRUE) %>% setnames(., c("chr", "CpG"))), by="chr") %>% 
  .[, frakcija := targets/CpG] %>% 
  .[, chr := factor(chr, levels=paste0("chr", c(1:19, "X", "Y")))] 

ggplot(tmp, aes(chr, frakcija, fill=sample)) +
  geom_col(position="dodge") +
  theme_bw() +
  scale_fill_brewer(palette="Dark2") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position="bottom") +
  ylab("Targets, %") +
  ggtitle("Targets (cov>0) per chromosome") +
  scale_y_continuous(labels = scales::percent)

```

## Bin'u lygio duomenys 

Correlations (using bins of 2kb). Targets number per bin used here. 

```{r}
suma_2 <- function(x){sum(x>0, na.rm=TRUE)}
bin_size <- 2000
coverages$ID <- paste0(coverages$chr, "_", floor(as.numeric(coverages$start)/bin_size))
binai <- coverages[, lapply(.SD, sum, na.rm=TRUE), by = "ID", .SDcols=samples2do] 
binai_taikiniai <- coverages[, lapply(.SD, suma_2), by = "ID", .SDcols=samples2do] 

column_ha = HeatmapAnnotation(replicate = colnames(binai[, -1]) %>% strsplit(., "_") %>% sapply(., `[`, 2), 
                              condition = colnames(binai[, -1]) %>% strsplit(., "_") %>% sapply(., `[`, 1),
                              col = list(replicate = c("R1" = brewer.pal(n=9,"Greens")[2], "R2" = brewer.pal(n=9,"Greens")[4], "R3" = brewer.pal(n=9,"Greens")[6], "R4"=brewer.pal(n=9,"Greens")[8]), 
                                         condition = c("Het" = brewer.pal(n=3,"Set1")[1], "Hom" = brewer.pal(n=3,"Set1")[2], "WT" = brewer.pal(n=3,"Set1")[3])),
                              show_legend = c(FALSE, FALSE)           
                              )
row_ha = rowAnnotation(replicate = colnames(binai[, -1]) %>% strsplit(., "_") %>% sapply(., `[`, 2), 
                       condition = colnames(binai[, -1]) %>% strsplit(., "_") %>% sapply(., `[`, 1),
                       col = list(replicate = c("R1" = brewer.pal(n=9,"Greens")[2], "R2" = brewer.pal(n=9,"Greens")[4], "R3" = brewer.pal(n=9,"Greens")[6], "R4"=brewer.pal(n=9,"Greens")[8]), 
                                  condition = c("Het" = brewer.pal(n=3,"Set1")[1], "Hom" = brewer.pal(n=3,"Set1")[2], "WT" = brewer.pal(n=3,"Set1")[3]))
                              )
tmp <- cor((as.data.table(binai_taikiniai) %>% .[, ID := NULL])) 
Heatmap(tmp, name="pearson", 
          top_annotation = column_ha, 
          right_annotation = row_ha,
          show_row_names=FALSE,
          show_column_names=TRUE,
          column_title = "Pearson correlation on bins",
          cell_fun = function(j, i, x, y, w, h, col) { 
          grid.text(round(tmp[i, j], 2), x, y)}
          )
saveRDS(list(tmp, column_ha, row_ha), paste0(outdatadir, "data_heatmapCor.RDS"))
```


Summed bin coverage used here.
```{r}
tmp <- cor((as.data.table(binai) %>% .[, ID := NULL])) 
Heatmap(tmp, name="pearson", 
          top_annotation = column_ha, 
          right_annotation = row_ha,
          show_row_names=FALSE,
          show_column_names=TRUE,
          column_title = "Pearson correlation on bins",
          cell_fun = function(j, i, x, y, w, h, col) { 
          grid.text(round(tmp[i, j], 2), x, y)}
          )

tmp <- (as.data.table(binai))
tmp_table <- data.frame(matrix(nrow=length(names(tmp)[-1]), ncol=length(names(tmp)[-1])))
colnames(tmp_table) <- names(tmp)[-1]
rownames(tmp_table) <- names(tmp)[-1]
```

Jaccard using 2kb bins. All bins with at least one target counted. 
```{r}
tmp <- foreach(i=names(tmp)[-1], .combine="rbind") %do% {
    foreach(j=names(tmp)[-1], .combine="rbind") %do% { 
    tmp_table[i, j] <- length(intersect(coverages[get(i)>0, ID], coverages[get(j)>0, ID]))/length(union(coverages[get(i)>0, ID], coverages[get(j)>0, ID]))
} }

column_ha = HeatmapAnnotation(replicate = colnames(tmp_table) %>% strsplit(., "_") %>% sapply(., `[`, 2), 
                              condition = colnames(tmp_table) %>% strsplit(., "_") %>% sapply(., `[`, 1),
                              col = list(replicate = c("R1" = brewer.pal(n=9,"Greens")[2], "R2" = brewer.pal(n=9,"Greens")[4], "R3" = brewer.pal(n=9,"Greens")[6], "R4"=brewer.pal(n=9,"Greens")[8]), 
                                         condition = c("Het" = brewer.pal(n=3,"Set1")[1], "Hom" = brewer.pal(n=3,"Set1")[2], "WT" = brewer.pal(n=3,"Set1")[3])),
                              show_legend = c(FALSE, FALSE)           
                              )
row_ha = rowAnnotation(replicate = colnames(tmp_table) %>% strsplit(., "_") %>% sapply(., `[`, 2), 
                       condition = colnames(tmp_table) %>% strsplit(., "_") %>% sapply(., `[`, 1),
                       col = list(replicate = c("R1" = brewer.pal(n=9,"Greens")[2], "R2" = brewer.pal(n=9,"Greens")[4], "R3" = brewer.pal(n=9,"Greens")[6], "R4"=brewer.pal(n=9,"Greens")[8]), 
                                  condition = c("Het" = brewer.pal(n=3,"Set1")[1], "Hom" = brewer.pal(n=3,"Set1")[2], "WT" = brewer.pal(n=3,"Set1")[3]))
                              )

Heatmap(tmp_table, name="Jaccard", 
          top_annotation = column_ha, 
          right_annotation = row_ha,
          show_row_names=FALSE,
          show_column_names=TRUE,
          column_title = "Jaccard on bins",
          cell_fun = function(j, i, x, y, w, h, col) { 
          grid.text(round(tmp_table[i, j], 2), x, y)}
          )
```


Simple PCA: two variants done. Var1: coverages sum per bin. Var2: number of targets per bin. 

```{r}
pca <- binai[, -1] %>% t %>% prcomp(., center=FALSE, scale=FALSE)
d <- as.data.table(pca$x, keep.rownames=TRUE)

p1 <- d %>% 
  .[, rep := str_extract( as.character(rn), "R[1-4]")] %>% 
  .[, condition := strsplit(as.character(rn), "_") %>% sapply(., `[`, 1)] %>% 
  ggplot(aes(PC1, PC2, colour=condition, shape=rep)) + 
    geom_point(size=3) +
    theme_bw() +
    scale_colour_brewer(palette="Dark2") +
    ggtitle("Cov. sum per bin.") +
    xlab(paste0("PC1, ", round(summary(pca)$importance[2, 1]*100, 2), "%")) +
    ylab(paste0("PC2, ", round(summary(pca)$importance[2, 2]*100, 2), "%")) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
          legend.position="bottom"
          )  

pca <- binai_taikiniai[, -1] %>% t %>% prcomp(., center=FALSE, scale=FALSE)
d <- as.data.table(pca$x, keep.rownames=TRUE)

p2 <- d %>% 
  .[, rep := str_extract( as.character(rn), "R[1-4]")] %>% 
  .[, condition := strsplit(as.character(rn), "_") %>% sapply(., `[`, 1)] %>% 
  ggplot(aes(PC1, PC2, colour=condition, shape=rep)) + 
    geom_point(size=3) +
    theme_bw() +
    scale_colour_brewer(palette="Dark2") +
    ggtitle("Cov. tergets per bin.") +
    xlab(paste0("PC1, ", round(summary(pca)$importance[2, 1]*100, 2), "%")) +
    ylab(paste0("PC2, ", round(summary(pca)$importance[2, 2]*100, 2), "%")) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
          legend.position="bottom"
          )  


binai_m <- coverages[, lapply(.SD, sum, na.rm=TRUE), by = "ID", .SDcols=samples2do_m]
binai_taikiniai_m <- coverages[, lapply(.SD, suma_2), by = "ID", .SDcols=samples2do_m]

pca <- binai_m[, -1] %>% t %>% prcomp(., center=FALSE, scale=FALSE)
d <- as.data.table(pca$x, keep.rownames=TRUE)
p3 <- d %>% 
  .[, condition := strsplit(as.character(rn), "_") %>% sapply(., `[`, 1)] %>% 
  ggplot(aes(PC1, PC2, colour=condition)) + 
    geom_point(size=3) +
    theme_bw() +
    scale_colour_brewer(palette="Dark2") +
    ggtitle("Cov. sum per bin.") +
    xlab(paste0("PC1, ", round(summary(pca)$importance[2, 1]*100, 2), "%")) +
    ylab(paste0("PC2, ", round(summary(pca)$importance[2, 2]*100, 2), "%")) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
          legend.position="bottom")  

pca <- binai_taikiniai_m[, -1] %>% t %>% prcomp(., center=FALSE, scale=FALSE)
d <- as.data.table(pca$x, keep.rownames=TRUE)
p4 <- d %>% 
  .[, condition := strsplit(as.character(rn), "_") %>% sapply(., `[`, 1)] %>% 
  ggplot(aes(PC1, PC2, colour=condition)) + 
    geom_point(size=3) +
    theme_bw() +
    scale_colour_brewer(palette="Dark2") +
    ggtitle("Cov. tergets per bin.") +
    xlab(paste0("PC1, ", round(summary(pca)$importance[2, 1]*100, 2), "%")) +
    ylab(paste0("PC2, ", round(summary(pca)$importance[2, 2]*100, 2), "%")) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
          legend.position="bottom")  
```


```{r}
(p1 | p2) / (p3 + p4)  +  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
```

## Some analysis


Fraction of CpGs identified on different elements as well as their average coverage.  

About the question marks: "The rules for assigning question marks are arbitrary; currently question marks are used when a
match shows a 2-fold lower or a 1.5-fold higher divergence level as expected for a repeat at the boundary."

```{r, fig.height=9}
tmp <- readRDS(paste0("output/code/PrepAllData//dAnnotations.RDS"))
repeatai <- tmp[["repeatai"]]
mcols(repeatai)$type <- paste0(mcols(repeatai)$Name, "_", mcols(repeatai)$Class, "_", mcols(repeatai)$Familly)
annotations <- tmp[["anotacijos"]]
anotacijos <- c(annotations, repeatai)

coverages_gr <- coverages %>% 
  .[, end := start] %>% 
  makeGRangesFromDataFrame(., keep.extra.column=TRUE)

feat2do_genes <- c("mm10_cpg_islands", "mm10_CTCF", "mm10_EPDpromotersNC", "mm10_genes_3UTRs", "mm10_genes_cds", "mm10_genes_firstexons", "mm10_genes_introns", "mm10_lncrna_gencode", "mm10_PoisedEnhancers_Atlas", "mm10_processedPseudogene", "mm10_Silencer_E14", "mm10_superEnhancer", "mm10_EPDpromoters", "mm10_Silencer_mESC", "mm10_transcriptsCoding")

gff <- import("/mnt/store/annotations/MusMusculus_mm10_Ensembl/ENCODE/gencode.vM23.annotation.gtf")

tmp <- annotations[mcols(annotations)$type == "mm10_genes_3UTRs"]
mcols(tmp)$type <- "3UTRs"
tmp_annotations <- copy(tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_genes_5UTRs"]
mcols(tmp)$type <- "5UTRs"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_lncrna_gencode"]
mcols(tmp)$type <- "lncRNA_gencode"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_genes_exons"]
mcols(tmp)$type <- "exons"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_genes_introns"]
mcols(tmp)$type <- "introns"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_EPDpromoters"]
mcols(tmp)$type <- "promoterEPD"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_EPDpromotersNC"]
mcols(tmp)$type <- "promoter_NC_EPD"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_transcriptsCoding"]
mcols(tmp)$type <- "codingTranscripts"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"][countOverlaps(annotations[mcols(annotations)$type == "mm10_cpg_islands"], annotations[mcols(annotations)$type == "mm10_EPDpromoters"]) > 0]
mcols(tmp)$type <- "CGI promoter"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"][countOverlaps(annotations[mcols(annotations)$type == "mm10_cpg_islands"], annotations[mcols(annotations)$type == "mm10_genes_intergenic"]) > 0]
mcols(tmp)$type <- "CGI intergenic"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"][countOverlaps(annotations[mcols(annotations)$type == "mm10_cpg_islands"], annotations[mcols(annotations)$type == "mm10_transcriptsCoding"]) > 0]
mcols(tmp)$type <- "CGI intragenic"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_shelves"]
mcols(tmp)$type <- "CGI shelves"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_shores"]
mcols(tmp)$type <- "CGI shores"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- annotations[mcols(annotations)$type == "mm10_cpg_islands"]
mcols(tmp)$type <- "CGI all"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- gff[mcols(gff)$gene_type == "miRNA"] 
mcols(tmp) <- NULL 
mcols(tmp)$type <- "miRNA"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- gff[mcols(gff)$gene_type == "snoRNA"]
mcols(tmp) <- NULL 
mcols(tmp)$type <- "snoRNA"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- gff[mcols(gff)$gene_type == "snRNA"]
mcols(tmp) <- NULL 
mcols(tmp)$type <- "snRNA"
tmp_annotations <- c(tmp_annotations, tmp)

feat2do_genes <- c("3UTRs", "5UTRs", "lncRNA_gencode", "exons", "introns", "promoterEPD", "promoter_NC_EPD", "codingTranscripts", "CGI promoter", "CGI intergenic", "CGI intragenic", "CGI shelves", "CGI shores", "CGI all", "miRNA", "snoRNA", "snRNA")



suma <- function(x) {sum(x>0, na.rm=TRUE)}

frakcijos_gen <- foreach(i=feat2do_genes, .combine="rbind") %do% {
  elementai <- tmp_annotations[mcols(tmp_annotations)$type == i] %>% reduce
  nCG <- countOverlaps(coverages_gr, elementai) %>% sum
  frakcija <- foreach(j=samples2do_m, .combine="c") %do% {
    (countOverlaps(coverages_gr[elementMetadata(coverages_gr)[, j]>0], elementai) %>% suma)/nCG
  }
  names(frakcija) <- samples2do_m
  return(frakcija)
}
rownames(frakcijos_gen) <- feat2do_genes

coveragas_gen <- foreach(i=feat2do_genes, .combine="rbind") %do% {

  elementai <- tmp_annotations[mcols(tmp_annotations)$type == i] %>% reduce
  nCG <- countOverlaps(coverages_gr, elementai) %>% sum
 
  coveragas <- foreach(j=samples2do_m, .combine="c") %do% {
    coverages_gr[elementMetadata(coverages_gr)[, j]>0][countOverlaps(coverages_gr[elementMetadata(coverages_gr)[, j]>0], elementai)>0] %>% 
      as.data.table() %>% 
      .[, j, with=FALSE] %>% 
      colMeans()
  }
  names(coveragas) <- samples2do_m
  return(coveragas)
}
rownames(coveragas_gen) <- feat2do_genes 

saveRDS(list(frakcijos_gen, coveragas_gen), paste0(outdatadir, "data_ElementFrac.RDS"))

p1 <- frakcijos_gen %>% 
  melt() %>% 
  as.data.table() %>%
  .[, Var1 := gsub("mm10_", "", Var1)] %>% 
  .[, Var1 := gsub("_", "\n", Var1)] %>% 
  ggplot(aes(Var1, value, fill=Var2)) +
    geom_col(position="dodge") +
    coord_flip() +
    theme_bw() +
    xlab("Element") +
    ylab("Amount of CpGs, %") +
    labs(fill="Mutant") +
    scale_fill_brewer(palette="Dark2") +
    theme(legend.position="bottom") +
    scale_y_continuous(labels = scales::percent) +
    ggtitle("Genome elements. Target fraction")

p3 <- coveragas_gen %>% 
  melt() %>% 
  as.data.table() %>% 
  .[, Var1 := gsub("mm10_", "", Var1)] %>% 
  .[, Var1 := gsub("_", "\n", Var1)] %>%   
  ggplot(aes(Var1, value, fill=Var2)) +
    geom_col(position="dodge") +
    coord_flip() +
    theme_bw() +
    xlab("Element") +
    ylab("Mean coverage") +
    labs(fill="Mutant") +
    scale_fill_brewer(palette="Dark2") +
    theme(legend.position="bottom") +
    ggtitle("Genome elements. Mean coverage")
``` 

```{r, fig.height=9}
tmp <- repeatai[mcols(repeatai)$Class == "DNA"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "DNA"
tmp_annotations <- copy(tmp)

tmp <- repeatai[mcols(repeatai)$Class == "SINE"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "SINE"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "LINE"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "LINE"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "LTR"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "LTR"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "Simple_repeat"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "Simples"
tmp_annotations <- c(tmp_annotations, tmp)


tmp <- repeatai[mcols(repeatai)$Class == "Satellite"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "Satellite"
tmp_annotations <- c(tmp_annotations, tmp)

tmp <- repeatai[mcols(repeatai)$Class == "Low_complexity"]
mcols(tmp) <- NULL
mcols(tmp)$type <- "Low_complexity"
tmp_annotations <- c(tmp_annotations, tmp)

reps2do <- c("DNA", "SINE", "LINE", "LTR", "Simples", "Satellite", "Low_complexity")

suma <- function(x) {sum(x>0)}

frakcijos_rep <- foreach(i=reps2do, .combine="rbind") %do% {
  elementai <- tmp_annotations[tmp_annotations$type == i] %>% reduce
  nCG <- countOverlaps(coverages_gr, elementai) %>% sum
  frakcija <- foreach(j=samples2do_m, .combine="c") %do% {
    (countOverlaps(coverages_gr[elementMetadata(coverages_gr)[, j]>0], elementai) %>% suma)/nCG
  }
  names(frakcija) <- samples2do_m
  return(frakcija)
}

rownames(frakcijos_rep) <- reps2do

p2 <- frakcijos_rep %>% 
  melt() %>% 
  as.data.table() %>% 
  .[, Var1 := gsub("mm10_", "", Var1)] %>% 
  .[, Var1 := gsub("_", "\n", Var1)] %>% 
  ggplot(aes(Var1, value, fill=Var2)) +
    geom_col(position="dodge") +
    coord_flip() +
    theme_bw() +
    xlab("Element") +
    ylab("Amount of CpGs, %") +
    labs(fill="Mutant") +
    scale_fill_brewer(palette="Dark2") +
    theme(legend.position="bottom") +
    scale_y_continuous(labels = scales::percent) +
    ggtitle("Repeats elements. Target fraction")

coveragas_rep <- foreach(i=reps2do, .combine="rbind") %do% {
  elementai <- tmp_annotations[mcols(tmp_annotations)$type == i] %>% reduce
  nCG <- countOverlaps(coverages_gr, elementai) %>% sum
 
  coveragas <- foreach(j=samples2do_m, .combine="c") %do% {
    coverages_gr[elementMetadata(coverages_gr)[, j]>0][countOverlaps(coverages_gr[elementMetadata(coverages_gr)[, j]>0], elementai)>0] %>% 
      as.data.table() %>% 
      .[, j, with=FALSE] %>% 
      colMeans()
  }
  names(coveragas) <- samples2do_m
  return(coveragas)
}

rownames(coveragas_rep) <- reps2do

p4 <- coveragas_rep %>% 
  melt() %>% 
  as.data.table() %>% 
  .[, Var1 := gsub("mm10_", "", Var1)] %>% 
  .[, Var1 := gsub("_", "\n", Var1)] %>%   
  ggplot(aes(Var1, value, fill=Var2)) +
    geom_col(position="dodge") +
    coord_flip() +
    theme_bw() +
    xlab("Element") +
    ylab("Mean coverage") +
    labs(fill="Mutant") +
    scale_fill_brewer(palette="Dark2") +
    theme(legend.position="bottom")  +
    ggtitle("Repeats. Mean coverage")


saveRDS(list(frakcijos_rep, coveragas_rep), paste0(outdatadir, "data_RepeatsFrac.RDS"))
```


```{r, fig.width=12, fig.height=8}
p1 | p2 
```



```{r, fig.width=12, fig.height=8}
p3 | p4
```
