```{r}
library(pacman)
p_load(data.table, dplyr, ggplot2, rtracklayer, RColorBrewer, scales, foreach, 
viridis, annotatr, stringr, GGally, EnrichedHeatmap, circlize, corrplot, patchwork)
options(scipen=999)
knitr::opts_chunk$set(fig.width=9, fig.height=7)
dir.create(outdatadir, recursive=TRUE)
source("code/common.R")
```

# WGBS vs RRBS {.tabset}

BlackListed regions are present/counted. 

```{r}
samples2do <- c("RRBS_homo", "RRBS_hetero", "WGBS_KO", "WGBS_hetero", "WGBS_homo", "WGBS_WT")
tmp <- readRDS(paste0("output/code/PrepAllData//dAnnotations.RDS"))
repeatai <- tmp[["repeatai"]]
mcols(repeatai)$type <- paste0(mcols(repeatai)$Name, "_", mcols(repeatai)$Class, "_", mcols(repeatai)$Familly)
annotations <- tmp[["anotacijos"]]
anotacijos <- c(annotations, repeatai)

tmp <- readRDS(paste0("output/code/PrepAllData//WGBS_vs_RRBS_data.RDS"))
met_gr_full <- tmp[["methylation_gr_full"]]
met_gr <- tmp[["methylation_gr_th"]]

total_cov <- tmp[["raw"]] %>% .[, c("ID", paste0(samples2do, "_cov")), with=FALSE]
total_cov[is.na(total_cov)] <- 0
total_raw <- tmp[["raw"]]

methylation <- tmp[["methylation_gr_th"]] %>% as.data.table() %>% 
  .[, `:=` (seqnames = NULL, start = NULL, end = NULL, width = NULL, strand = NULL)]
methylation_full <- tmp[["methylation_gr_full"]] %>% as.data.table()  %>% 
  .[, `:=` (seqnames = NULL, start = NULL, end = NULL, width = NULL, strand = NULL)]

rm(tmp)
gc()
```

## Library stats 

```{r}
# Number of target CG by coverage 
rezu <- foreach(i=c(1, 2, 3, 5, 7, 10, 15), .combine="rbind") %do% { 
  foreach(j=paste0(samples2do, "_cov"), .combine="rbind") %do% {
    data.frame(kiekis=nrow(total_cov[get(j) >= i,  ]), samplas=j, threshold=i) 
  }
}

rezu %>% 
  as.data.table() %>%
  .[, threshold := as.character(threshold)] %>% 
  .[, threshold := factor(threshold, levels = paste0(c(1, 2, 3, 5, 7, 10, 15))) ] %>% 
  ggplot(aes(samplas, kiekis, fill=threshold)) +
    geom_col(position="dodge") +
    theme_bw() +
    ggtitle("Number of targets") +
    ylab("Targets") +
    xlab("Sample") +
    scale_fill_brewer(palette="Dark2") +
    labs(fill="Coverage\nthreshold") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6))

# Number of reads 

if(!file.exists(paste0(outdatadir, "libSizes.RDS"))) {
  bs_wt <- system(paste0("zcat ", "/mnt/store/sequencingRawData/2022/22.03.25_erc_wgbs/dWT_R1_val_1.fq.gz", " | wc -l"), intern=TRUE)
  bs_hetero <- system(paste0("zcat ", "/mnt/store/sequencingRawData/2022/22.03.25_erc_wgbs/Da31_R1_val_1.fq.gz", " | wc -l"), intern=TRUE)
  bs_KO <- system(paste0("zcat ", "/mnt/store/sequencingRawData/2022/22.02.04_erc_wgbs/KO3_bWGS_R1_val_1.fq.gz", " | wc -l"), intern=TRUE)
  bs_homo <- system(paste0("zcat ", "/mnt/store/sequencingRawData/2022/22.02.04_erc_wgbs/B2_bWGS_R1_val_1.fq.gz", " | wc -l"), intern=TRUE)
  rrbs_homo <- system(paste0("zcat ", "/mnt/store/sequencingRawData/2022/22.02.04_erc_wgbs/B2_RRBS_R1_val_1.fq.gz", " | wc -l"), intern=TRUE)
  rrbs_hetero <- system(paste0("zcat ", "/mnt/store/sequencingRawData/2022/22.02.04_erc_wgbs/dA32_R2_val_2.fq.gz", " | wc -l"), intern=TRUE)
  tmp <- c(bs_wt=bs_wt, bs_hetero=bs_hetero, bs_KO=bs_KO, bs_homo=bs_homo, rrbs_homo=rrbs_homo, rrbs_hetero=rrbs_hetero) 
  saveRDS(tmp, paste0(outdatadir, "libSizes.RDS"))  
} else {tmp <- readRDS(paste0(outdatadir, "libSizes.RDS"))}

melt(tmp) %>%  
  as.data.table(., keep.rownames=TRUE) %>% 
  .[, type := "WGBS"] %>% 
  .[grepl("rrbs", rn), type := "RRBS"] %>% 
  .[, value := as.numeric(value)] %>% 
  .[, value := value / 4] %>% 
  ggplot(aes(rn, value)) +
    geom_col() +
    theme_bw() +
    ylab("Reads") +
    xlab("Sample") +
    ggtitle("Raw library size") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) +
    facet_wrap(~type, scales="free")
```


## Binned data

Genome was divided into bins (100 bp, 500 bp, 1 kb, 2 kb), methylation was averaged per bin and used to calculate pearson correlation. All coverages and all methylation levels used.
For PCA analysis, there are two variants: one were all bins were used and second were only bins with RRBS signal (coverage not 0 in at least on RRBS sample) were used. 

All CpG with coverage <5 not counted. 

```{r}
bin_size <- 100
binai <- methylation %>% 
  .[, bin_id := paste0( strsplit(ID, "_") %>% sapply(., `[`, 1), "_", ceiling((strsplit(ID, "_") %>% sapply(., `[`, 2) %>% as.numeric)/bin_size))] %>% 
  .[, lapply(.SD, mean, na.rm=TRUE), by="bin_id", .SDcols=c("RRBS_homo_met", "RRBS_hetero_met", "WGBS_KO_met",  "WGBS_WT_met", "WGBS_hetero_met", "WGBS_homo_met")] 
p01kb <- plotCor(binai, "Bins (100bp) level correlation")
p01kb_PCA1 <- plotPCA(binai[, c("bin_id", paste0(samples2do[grepl("WGBS", samples2do)], "_met")), with=FALSE], "100bp", samples2do[grepl("WGBS", samples2do)])
p01kb_PCA2 <- plotPCA(binai, "100bp", samples2do)

bin_size <- 500
binai <- methylation %>% 
  .[, bin_id := paste0( strsplit(ID, "_") %>% sapply(., `[`, 1), "_", ceiling((strsplit(ID, "_") %>% sapply(., `[`, 2) %>% as.numeric)/bin_size))] %>% 
  .[, lapply(.SD, mean, na.rm=TRUE), by="bin_id", .SDcols=c("RRBS_homo_met", "RRBS_hetero_met", "WGBS_KO_met",  "WGBS_WT_met", "WGBS_hetero_met", "WGBS_homo_met")] 
p05kb <- plotCor(binai, "Bins (500bp) level correlation")
p05kb_PCA1 <- plotPCA(binai[, c("bin_id", paste0(samples2do[grepl("WGBS", samples2do)], "_met")), with=FALSE], "500bp", samples2do[grepl("WGBS", samples2do)])
p05kb_PCA2 <- plotPCA(binai, "500bp", samples2do)

bin_size <- 1000
binai <- methylation %>% 
  .[, bin_id := paste0( strsplit(ID, "_") %>% sapply(., `[`, 1), "_", ceiling((strsplit(ID, "_") %>% sapply(., `[`, 2) %>% as.numeric)/bin_size))] %>% 
  .[, lapply(.SD, mean, na.rm=TRUE), by="bin_id", .SDcols=c("RRBS_homo_met", "RRBS_hetero_met", "WGBS_KO_met",  "WGBS_WT_met", "WGBS_hetero_met", "WGBS_homo_met")] 
p1kb <- plotCor(binai, "Bins (1000bp) level correlation")
p1kb_PCA1 <- plotPCA(binai[, c("bin_id", paste0(samples2do[grepl("WGBS", samples2do)], "_met")), with=FALSE], "1000bp", samples2do[grepl("WGBS", samples2do)])
p1kb_PCA2 <- plotPCA(binai, "1000bp", samples2do)

bin_size <- 2000
binai <- methylation %>% 
  .[, bin_id := paste0( strsplit(ID, "_") %>% sapply(., `[`, 1), "_", ceiling((strsplit(ID, "_") %>% sapply(., `[`, 2) %>% as.numeric)/bin_size))] %>% 
  .[, lapply(.SD, mean, na.rm=TRUE), by="bin_id", .SDcols=c("RRBS_homo_met", "RRBS_hetero_met", "WGBS_KO_met",  "WGBS_WT_met", "WGBS_hetero_met", "WGBS_homo_met")] 
p2kb <- plotCor(binai, "Bins (2000bp) level correlation")
p2kb_PCA1 <- plotPCA(binai[, c("bin_id", paste0(samples2do[grepl("WGBS", samples2do)], "_met")), with=FALSE], "2000bp", samples2do[grepl("WGBS", samples2do)])
p2kb_PCA2 <- plotPCA(binai, "2000bp", samples2do)

saveRDS(list(binai=binai), paste0(outdatadir, "bins2kb_CorScat.RDS"))

p <- (p01kb | p05kb) / (p1kb | p2kb) + plot_layout(guides = "collect") & theme(legend.position = 'bottom')
p 

p <- (p01kb_PCA1 | p01kb_PCA2) / ( p05kb_PCA1 | p05kb_PCA2) / (p1kb_PCA1 | p1kb_PCA2) / ( p2kb_PCA1 | p2kb_PCA2)
p <- p + plot_layout(guides = "collect") & theme(legend.position = 'bottom')
p
```

## Whole genome

Per CpG level data. Using threshold that are indicated.. 

### Correlations and density 

```{r}
p2 <- methylation_full[, paste0(samples2do, "_met"), with=FALSE] %>% 
  melt() %>% 
  .[, variable := gsub("_met", "", variable)] %>% 
  .[, tipas := str_extract(variable, "..BS")] %>% 
  ggplot(aes(x=value, colour=variable, fill=variable)) +
    geom_density(key_glyph = "rect", alpha=0.5) +
    theme_bw() +
    xlab("methylation") +
    facet_wrap(~tipas, scales="free") +
    scale_colour_brewer(palette="Dark2", name="sample") +
    scale_fill_brewer(palette="Dark2", name="sample", guide = 'none') +
    labs(subtitle="Density. All CG", colour="sample") +
    theme(legend.position="bottom") +
    guides(colour = guide_legend(override.aes = list(alpha = 1)), fill = guide_legend(override.aes = list(alpha = 1)))


th <- 4
p3 <- methylation[, paste0(samples2do, "_met"), with=FALSE] %>% 
  melt() %>% 
  .[, variable := gsub("_met", "", variable)] %>% 
  .[, tipas := str_extract(variable, "..BS")] %>% 
  ggplot(aes(x=value, colour=variable, fill=variable)) +
    geom_density(key_glyph = "rect", alpha=0.5) +
    theme_bw() +
    xlab("methylation") +
    facet_wrap(~tipas, scales="free") +
    scale_colour_brewer(palette="Dark2", name="sample") +
    scale_fill_brewer(palette="Dark2", name="sample", guide = 'none') +
    theme(legend.position="bottom") +
    guides(colour = guide_legend(override.aes = list(alpha = 1)), fill = guide_legend(override.aes = list(alpha = 1)))

tmp <- methylation[, paste0(samples2do, "_met"), with=FALSE] %>% 
#head(10000) %>% 
  melt() %>% 
  .[, variable := gsub("_met", "", variable)] %>% 
  .[, tipas := str_extract(variable, "..BS")]  
saveRDS(tmp, paste0(outdatadir, "DensityPlot.RDS"))

p <- (p2 | p3)  + plot_layout(guides = "collect") & theme(legend.position = 'bottom')
p 
```


CG level correlation, Cov > 4

```{r`}
methylation[, c("ID", paste0(samples2do, "_met")), with=FALSE] %>% 
 plotCor(., "CpG level correlation. Cov>4")

```

### Per chromosome data 

Methylation and coverage per chromosome. Using only WGBS data. 

```{r}
methylation_full %>% 
  as.data.table %>% 
  .[, chr := str_extract(ID, "chr[0-9XY]+")] %>% 
  .[, c(paste0(samples2do, "_met"), "chr"), with=FALSE] %>% 
  melt() %>% 
  ggplot(aes(chr, value)) +
    geom_violin() +
    geom_boxplot(width=0.1, outlier.shape=NA) +
    facet_wrap(~variable) +
    theme_bw() +
    labs(subtitle="Methylation. All CpG") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

th <- 4
tmp <- methylation %>% 
  as.data.table %>% 
  .[, chr := str_extract(ID, "chr[0-9XY]+")] %>% 
  .[, c(paste0(samples2do, "_met"), "chr"), with=FALSE] %>% 
  melt() %>% 
  as.data.table() %>% 
  .[, variable := factor(variable, levels=paste0(samples2do, "_met"))] %>%  
  .[, chr := factor(chr, levels=c(paste0("chr", c(1:19, "X", "Y"))))]
saveRDS(tmp, paste0(outdatadir, "perChromosomeData.RDS"))  
tmp %>% 
  ggplot(aes(chr, value)) +
    geom_violin() +
    geom_boxplot(width=0.1, outlier.shape=NA) +
    facet_wrap(~variable) +
    theme_bw() +
    labs(subtitle="Methylation. All CpG cov > 4") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### Methylation groups

CpGs were divided into groups based on methylation levels and a simple stacked barplot was plotted. Groups: 

No signal = no reads or less than 5 reads 
0-20 - methylation between 0 and 20. At least 5 reads. 

```{r}
get_groups <- function(x, y, th=4) {
  x <- unlist(x)
  x[is.na(x)] <- 0
  y <- unlist(y)
  y[is.na(y)] <- 0
  return(data.frame(nuliniai=sum(y <= th), mazai=sum(x[y>th] <= 20),  daugiau=sum((x[y>th] > 20) & (x[y>th] <=40)), 
                    dardaugiau=sum((x[y>th] > 40) & (x[y>th] <=60)), dardardaugiau=sum((x[y>th] > 60) & (x[y>th] <=80)), 
                    labaidaug=sum((x[y>th] > 80) & (x[y>th] <=95)), begalo=sum((x[y>th] > 95))) %>% as.data.table())  
}

tmp <- foreach(i=samples2do, .combine="rbind") %do% {
  get_groups(methylation[, paste0(i, "_met"), with=FALSE], total_cov[, paste0(i, "_cov"), with=FALSE]) %>% as.data.table %>% .[, samplas := i]
}
viso <- as.data.table(tmp) %>% .[1, ] %>% .[, samplas := NULL] %>% sum
tmp %>% 
  melt() %>% 
  .[, fr := value/viso] %>% 
  .[, variable := factor(variable, levels=c("begalo", "labaidaug", "dardardaugiau", "dardaugiau", "daugiau", "mazai", "nuliniai"), 
                                   labels=c("(95-100]", "(80-95]", "(60-80]", "(40-60]", "(20-40]", "(0-20]", "0"))] %>% 
  .[, technology := str_extract(samplas, "..BS")] %>%  
  .[, type := strsplit(samplas, "_") %>% sapply(., `[`, 2)] %>% 
  .[, type := factor(type, levels=c("KO", "homo", "hetero", "WT"))] %>%  
  ggplot(aes(type, fr, fill=variable)) +
    geom_col(position="stack") +
    theme_bw() +
    scale_fill_brewer(palette="Dark2", name="Methylation") +
    facet_wrap(~technology, scales="free_x") +
    ylab("Fraction of all CpG")
```

### Total methylation

"Suminis metilinimas" - calculating total C/T reads per all CpGs. Using all CpGs (with any coverage). 

```{r}
tmp <- total_raw[, -1] %>% colSums(., na.rm=TRUE) %>% t %>% as.data.table()
temp <- data.frame(
  RRBS_homo=tmp$RRBS_homo_C/(tmp$RRBS_homo_C+tmp$RRBS_homo_T),
  RRBS_hetero=tmp$RRBS_hetero_C/(tmp$RRBS_hetero_C+tmp$RRBS_hetero_T), 
  WGBS_hetero=tmp$WGBS_hetero_C/(tmp$WGBS_hetero_C+tmp$WGBS_hetero_T),
  WGBS_homo=tmp$WGBS_homo_C/(tmp$WGBS_homo_C+tmp$WGBS_homo_T), 
  WGBS_WT=tmp$WGBS_WT_C/(tmp$WGBS_WT_C+tmp$WGBS_WT_T), 
  WGBS_KO=tmp$WGBS_KO_C/(tmp$WGBS_KO_C+tmp$WGBS_KO_T))  %>% 
    melt() %>% 
    as.data.table() %>% 
    .[, variable := factor(variable, levels=samples2do)] 
saveRDS(temp, paste0(outdatadir, "TotalMethylation.RDS"))

p1 <- ggplot(temp, aes(variable, value)) +
      geom_col() +
      theme_bw() +
      ggtitle("Total methylation") +
      ylab("methylation") +
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
            axis.title.x=element_blank()) +
      scale_y_continuous(labels = scales::percent)      
p1            
```

Same using only CG where coverage > 4. 

```{r}
total_raw_mod <- copy(total_raw)
total_raw_mod <- total_raw_mod %>% 
  .[RRBS_homo_cov < 5, `:=` (RRBS_homo_C = NA, RRBS_homo_T = NA)] %>% 
  .[RRBS_hetero_cov < 5, `:=` (RRBS_homo_C = NA, RRBS_homo_T = NA)] %>% 
  .[WGBS_hetero_cov < 5, `:=` (WGBS_hetero_C = NA, WGBS_hetero_T = NA)] %>% 
  .[WGBS_homo_cov < 5, `:=` (WGBS_homo_C = NA, WGBS_homo_T = NA)] %>% 
  .[WGBS_KO_cov < 5, `:=` (WGBS_KO_C = NA, WGBS_KO_T = NA)] %>% 
  .[WGBS_WT_cov < 5, `:=` (WGBS_WT_C = NA, WGBS_WT_T = NA)] 


tmp <- total_raw_mod[, -1] %>% colSums(., na.rm=TRUE) %>% t %>% as.data.table()
temp <- data.frame(
  RRBS_homo=tmp$RRBS_homo_C/(tmp$RRBS_homo_C+tmp$RRBS_homo_T),
  RRBS_hetero=tmp$RRBS_hetero_C/(tmp$RRBS_hetero_C+tmp$RRBS_hetero_T), 
  WGBS_hetero=tmp$WGBS_hetero_C/(tmp$WGBS_hetero_C+tmp$WGBS_hetero_T),
  WGBS_homo=tmp$WGBS_homo_C/(tmp$WGBS_homo_C+tmp$WGBS_homo_T), 
  WGBS_WT=tmp$WGBS_WT_C/(tmp$WGBS_WT_C+tmp$WGBS_WT_T), 
  WGBS_KO=tmp$WGBS_KO_C/(tmp$WGBS_KO_C+tmp$WGBS_KO_T))  %>% 
    melt() %>% 
    as.data.table() %>% 
    .[, variable := factor(variable, levels=samples2do)] 
saveRDS(temp, paste0(outdatadir, "TotalMethylationCov5.RDS"))

p2 <- ggplot(temp, aes(variable, value)) +
      geom_col() +
      theme_bw() +
      ggtitle("Total methylation") +
      ylab("methylation") +
      theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
            axis.title.x=element_blank()) +
      scale_y_continuous(labels = scales::percent)   
p2

feat <- "mm10_cpg_islands"
feat2do <- annotations[mcols(annotations)$type ==  feat]
total_raw_mod <- total_raw_mod %>% 
  .[, chr := strsplit(ID, "_") %>% sapply(., `[`, 1)] %>% 
  .[, start := strsplit(ID, "_") %>% sapply(., `[`, 2)] %>% 
  .[, end := strsplit(ID, "_") %>% sapply(., `[`, 2)] %>% 
  makeGRangesFromDataFrame(., keep.extra.column=TRUE)  

i <- countOverlaps(total_raw_mod, feat2do)
CGI_CG <- total_raw_mod[i > 0, ] 
neCGI_CG <- total_raw_mod[i == 0, ]

tmp <- CGI_CG %>% 
  as.data.table() %>% 
  .[, -(1:6)] %>% 
  colSums(., na.rm=TRUE) %>% 
  t %>% 
  as.data.table()

temp <- data.frame(
  RRBS_homo=tmp$RRBS_homo_C/(tmp$RRBS_homo_C+tmp$RRBS_homo_T),
  RRBS_hetero=tmp$RRBS_hetero_C/(tmp$RRBS_hetero_C+tmp$RRBS_hetero_T), 
  WGBS_hetero=tmp$WGBS_hetero_C/(tmp$WGBS_hetero_C+tmp$WGBS_hetero_T),
  WGBS_homo=tmp$WGBS_homo_C/(tmp$WGBS_homo_C+tmp$WGBS_homo_T), 
  WGBS_WT=tmp$WGBS_WT_C/(tmp$WGBS_WT_C+tmp$WGBS_WT_T), 
  WGBS_KO=tmp$WGBS_KO_C/(tmp$WGBS_KO_C+tmp$WGBS_KO_T))  %>% 
    melt() %>% 
    as.data.table() %>% 
    .[, variable := factor(variable, levels=samples2do)] 

saveRDS(temp, paste0(outdatadir, "TotalMethylationCov5_onlyCGI.RDS"))

tmp <- neCGI_CG %>% 
  as.data.table() %>% 
  .[, -(1:6)] %>% 
  colSums(., na.rm=TRUE) %>% 
  t %>% 
  as.data.table()

temp <- data.frame(
  RRBS_homo=tmp$RRBS_homo_C/(tmp$RRBS_homo_C+tmp$RRBS_homo_T),
  RRBS_hetero=tmp$RRBS_hetero_C/(tmp$RRBS_hetero_C+tmp$RRBS_hetero_T), 
  WGBS_hetero=tmp$WGBS_hetero_C/(tmp$WGBS_hetero_C+tmp$WGBS_hetero_T),
  WGBS_homo=tmp$WGBS_homo_C/(tmp$WGBS_homo_C+tmp$WGBS_homo_T), 
  WGBS_WT=tmp$WGBS_WT_C/(tmp$WGBS_WT_C+tmp$WGBS_WT_T), 
  WGBS_KO=tmp$WGBS_KO_C/(tmp$WGBS_KO_C+tmp$WGBS_KO_T))  %>% 
    melt() %>% 
    as.data.table() %>% 
   .[, variable := factor(variable, levels=samples2do)] 

saveRDS(temp, paste0(outdatadir, "TotalMethylationCov5_onlyNotCGI.RDS"))

```

```{r}
p1 | p2 
```

### Some more plots

Relationship between samples using 2d density plot. 
Using only those CpG that have coverage of at least 5 in both samples that are being plotted (this means that different CpGs are used in each plot)

```{r}
th <- 4
p1 <- methylation[total_cov$RRBS_hetero_cov > th & total_cov$RRBS_homo_cov > th, ] %>% 
  ggplot(aes(x=RRBS_homo_met, y=RRBS_hetero_met) ) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE, adjust = 5) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_bw() +
    theme(legend.position='none') 
  
p2 <- methylation[total_cov$WGBS_WT_cov > th & total_cov$WGBS_hetero_cov > th, ] %>% 
  ggplot(aes(x=WGBS_WT_met, y=WGBS_hetero_met) ) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE, adjust = 5) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_bw() +
    theme(legend.position='none')  

p3 <- methylation[total_cov$WGBS_WT_cov > th & total_cov$WGBS_homo_cov > th, ] %>% 
  ggplot(aes(x=WGBS_WT_met, y=WGBS_homo_met) ) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE, adjust = 5) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_bw() +
    theme(legend.position='none')  

p4 <- methylation[total_cov$WGBS_WT_cov > th & total_cov$WGBS_KO_cov > th, ] %>% 
  ggplot(aes(x=WGBS_WT_met, y=WGBS_KO_met) ) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE, adjust = 5) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_bw() +
    theme(legend.position='none')  

p5 <- methylation[total_cov$WGBS_hetero_cov > th & total_cov$WGBS_homo_cov > th, ] %>% 
  ggplot(aes(x=WGBS_hetero_met, y=WGBS_homo_met) ) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE, adjust = 5) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_bw() +
    theme(legend.position='none')  

p6 <- methylation[total_cov$WGBS_hetero_cov > th & total_cov$WGBS_KO_cov > th, ] %>% 
  ggplot(aes(x=WGBS_hetero_met, y=WGBS_KO_met) ) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE, adjust = 5) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_bw() +
    theme(legend.position='none')  


p7 <- methylation[total_cov$WGBS_homo_cov > th & total_cov$WGBS_KO_cov > th, ] %>% 
  ggplot(aes(x=WGBS_homo_met, y=WGBS_KO_met) ) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE, adjust = 5) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_bw() +
    theme(legend.position='none')  

(p2 | p3) / (p4 | p5) / (p6|p7) 

p1 
```

## Specific elements 

Fraction of CpGs that are covered by at least 5 reads in each genomic element by each sample. 

```{r}
dCG <- readRDS("/mnt/store/annotations/MusMusculus_mm10_Ensembl/CG_data_onC.RDS")
seqlevelsStyle(dCG) <- "UCSC"
mcols(dCG) <- NULL
dCG <- dCG[strand(dCG) == "+"]
mcols(dCG)$ID <- paste0(seqnames(dCG), "_", start(dCG),  "_", (start(dCG)+1))

cov_gr_full <- total_cov %>%  
  .[, chr := strsplit(ID, "_") %>% sapply(., `[`, 1)] %>% 
  .[, start := strsplit(ID, "_") %>% sapply(., `[`, 2)] %>% 
  .[, end := strsplit(ID, "_") %>% sapply(., `[`, 2)] %>% 
  makeGRangesFromDataFrame(., keep.extra.columns=TRUE)

get_CpG_per_elem <- function(samplas, cov_gr_full, elements2do) {
 tmp <- foreach(i=elements2do, .combine="rbind") %do% {
    total_CG <- sum(countOverlaps(dCG, anotacijos[grepl(i, mcols(anotacijos)$type)], ignore.strand=TRUE) > 0)
    sample_CG <- sum(countOverlaps(cov_gr_full[elementMetadata(cov_gr_full)[, samplas] >= 5], anotacijos[grepl(i, mcols(anotacijos)$type)], ignore.stran=TRUE) > 0)
    return(data.frame(total_CG, sample_CG, samplas, i))
      }
  return(tmp)
}

elements2do <- c("enhancers", "cpg_islands", "cpg_shelves", "cpg_shores", "genes_cds", "genes_5UTRs",  "genes_3UTRs", "genes_exons", "genes_firstexons", "genes_intergenic", "genes_introns", "genes_promoters")


rezu <- foreach(i=paste0(samples2do, "_cov"), .combine="rbind") %do% {
  get_CpG_per_elem(i, cov_gr_full, elements2do)
}

rezu %>% 
  as.data.table() %>% 
  .[, fraction := sample_CG/total_CG] %>% 
  ggplot(aes(i, fraction, fill=samplas)) +
    geom_col(position="dodge") +
    theme_bw() +
    ggtitle("Fraction of targeted CpGs") +
    scale_fill_brewer(palette="Dark2", name="sample") +
    theme(legend.position="bottom") +
    coord_flip()          

elements2do <- c("DNA", "LINE", "Low_complexity", "LTR", "RC", "Satellite", "Simple_repeat", "SINE", "Alu", "L1", "ERVK", "ERVL", "hAT", "L2", "MIR", "TcMar")

rezu <- foreach(i=paste0(samples2do, "_cov"), .combine="rbind") %do% {
  get_CpG_per_elem(i, cov_gr_full, elements2do)
}

rezu %>% 
  as.data.table() %>% 
  .[, fraction := sample_CG/total_CG] %>% 
  ggplot(aes(i, fraction, fill=samplas)) +
    geom_col(position="dodge") +
    theme_bw() +
    ggtitle("Fraction of targeted CpGs") +
    scale_fill_brewer(palette="Dark2", name="sample") +
    theme(legend.position="bottom") +
    coord_flip()          

```

## CGI  

Selecting CGI that seems to be highly methylated and then checking them in all samples. CGI were selected using average methylation per CGI (selected 5% of highest methylation CGI).
Using only unmasked CpG islands and CG coverage of at least 5. 

```{r}
feat <- "mm10_cpg_islands"
feat2do <- annotations[mcols(annotations)$type ==  feat]
feat2do <- feat2do[countOverlaps(feat2do, met_gr) > 0]
fo <- findOverlaps(feat2do, met_gr)

d <- feat2do[queryHits(fo)]
tmp <- cbind(mcols(feat2do[queryHits(fo)]), 
  elementMetadata(met_gr[subjectHits(fo)])[,paste0(samples2do, "_met")])
mcols(d) <- NULL
mcols(d) <- tmp
CGI_meth <- d %>% as.data.table() %>% .[, lapply(.SD, mean, na.rm=TRUE), by="id", .SDcols=paste0(samples2do, "_met")]

dd <- foreach(i=names(CGI_meth)[-1]) %do% {
  quant <- quantile(CGI_meth[, i, with=FALSE] %>% unlist, 0.95, na.rm=TRUE) 
  CGI_meth[get(i) > quant, id] %>% 
    as.data.table() %>% 
    setnames(., "NR") %>% 
    .[, sample := i] %>% 
    .[]
}
names(dd) <- names(CGI_meth)[-1]
```

Jaccard of identified CGIs 

```{r}
foreach(i=names(dd), .combine="rbind") %do% {
  foreach(j=names(dd), .combine="rbind") %do%  {
    data.table(JC=length(intersect(dd[[i]][, NR], dd[[j]][, NR])) / length(union(dd[[i]][, NR], dd[[j]][, NR])), samp1=i, samp2=j)    
  }
} %>% 
  ggplot(aes(samp1, samp2, fill=JC, label=round(JC, 2))) + 
    geom_tile(colour="black") +
    geom_text() +
    theme_bw() +
    scale_fill_viridis(limits=c(0, 1)) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

saveRDS(dd, paste0(outdatadir, "SelectedCGI.RDS"))
```

```{r}
tmp <- rbindlist(dd) %>% .[, NR] %>% unique
temp <- CGI_meth[id %in% tmp, -1]
temp[is.na(temp)] <- 0
Heatmap(temp)
```
